Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-01 awipev-CO2.Rmd
formatting

## Data processing
#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.

@@

* Serveur : awipev-co2 (193.50.85.104)
* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
* Pour se connecter à awipev-co2.obs-vlfr.fr
    + ssh awipev@awipev-co2.obs-vlfr.fr
* Intervention sur le serveur :
    + ssh awipev@awipev-co2.obs-vlfr.fr
    + rebooting Ubuntu server: sudo shutdown -r now
    + to check versions:
        - dpkg -l | grep shiny
        - dpkg -l | grep r-base
    + To update Ubuntu, R and its packages:
        - sudo su
        - apt-get upgrade
    + To restart shiny server: sudo systemctl restart shiny-server
        - update shiny server: follow procedure detailed on the shiny web page Data processing
* To install R packages:
    + ssh gattuso@o
    + sudo R (then password)
    + install.packages (tidyverse")

**crontab awipev@awipev-co2.obs-vlfr.fr**
Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
Pattern des commandes : # m h dom mon dow command

>>>>

### Data processing
#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
* calibrates pCO2 data
* data cleaning:
  + Argo Global Range Test.
  + filter salinities above 28
  + filter temperatures above 10
  + filter seaFET Volt (outliers)
  + filter seaFET pH (outliers)
  + filter durafet (outliers)
* Quality flags
    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data. 
* Despike using oce::despike with n=2, k=5761
* Files generated:
    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.

@@

* Serveur : awipev-co2 (193.50.85.104)
* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
* Pour se connecter à awipev-co2.obs-vlfr.fr
    + ssh awipev@awipev-co2.obs-vlfr.fr
* Intervention sur le serveur :
    + ssh awipev@awipev-co2.obs-vlfr.fr
    + rebooting Ubuntu server: sudo shutdown -r now
    + to check versions:
        - dpkg -l | grep shiny
        - dpkg -l | grep r-base
    + To update Ubuntu, R and its packages:
        - sudo su
        - apt-get upgrade
    + To restart shiny server: sudo systemctl restart shiny-server
        - update shiny server: follow procedure detailed on the shiny web page Data processing
* To install R packages:
    + ssh gattuso@awipev-co2.obs-vlfr.fr
    + sudo R (then password)
    + install.packages (tidyverse")

**crontab awipev@awipev-co2.obs-vlfr.fr**

Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
Pattern des commandes : # m h dom mon dow command
